Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2018-05-11 automatica/paper.tex
section 4

Note that a stable closed-loop model is not necessarily a safe model: 
indeed, the state values may leave the safe part of the state space while they converge
to the equilibrium, which is typical in the case of oscillatory convergent dynamics. 
%However, a safe system will always be stable.  
In~this work, the safety property is expressed as:
%
\begin{equation}
\label{eq:safetyliteral}
\phi_\mathit{safety} := \forall k\ge 0.\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
\end{equation}
%
%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
%
where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th
instant, respectively.  This means that the states will always be within an $n$-dimensional hyper-box.

@@

We analyze the case of hybrid-time models, 
namely where the plant dynamics evolve in continuous time, 
while the feedback dynamics evolve in discrete time.  
A new input value is accepted by the plant only at sample times $T_s$. \note{Confusing $T_s$ vs $T_d$.} 
%but implemented over the continuous-time plant dynamics.
%
%\note{Matrix K has not been introduced yet. }
\begin{theorem}
The expression
%
 \begin{align}
 \vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0, 
 \label{eq:cyber_feedback}
 \end{align}
%
with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}, $\mat{B}_T$ as in
\eqref{eq:continuous_tube_param}, and where $\mat{A}_d=\mat{A}_{T_s}$,
$\mat{B}_d=\mat{B}_{T_s}$ describe the discretized plant dynamics with
sample time $T_s$, is the state of the model
%
\begin{align*}
 \dot{\vec{x}}(t) = \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t), \quad 
 \vec{u}(t)=\mat{K}\vec{x}_k,  \,
 kT_s \leq t < (k+1)T_s \,. 
\end{align*}
%
\end{theorem}
\begin{proof}
%
Let $\mat{K}$ be a feedback controller such that
$\vec{u}_k=-\mat{K}\vec{x}_k$ at time $t=kT_s$.  Let the output of the
feedback system be a zero order holder such that
$\vec{u}(t'+kT_s)=\vec{u}(kT_s), \text{ for } 0 \leq t' < T_s$.  The closed
loop dynamics of the system between times $kT_s$ and $kT_s+T_s$ are
%
\begin{align*}
\vec{x}_{k,t'}=\mat{A}_{t'}\vec{x}_k-\mat{B}_{t'}\mat{K}\vec{x}_k = (\mat{A}_{t'}-\mat{B}_{t'}\mat{K})\vec{x}_k,
\end{align*}
where $0 \leq t' < T_s$
We further explore the dynamics across discrete time boundaries. Let $\mat{A}_d=\mat{A}_{T_s}$ and $\mat{B}_d=\mat{B}_{T_s}$
\begin{align*}
\vec{x}_{k}&=\vec{x}_{k-1,T_s}= (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}\\
\vec{x}_{k,T_s} &= (\mat{A}_d-\mat{B}_d\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}
\end{align*}
which accelerating results and setting $T=kT_s+t'$ becomes
\begin{align}
\label{eq:feedback_sampled_cont}
\vec{x}_{k} &= (\mat{A}_d-\mat{B}_d\mat{K}) ^k\vec{x}_0\\
\vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
\label{eq:feedback_cont}
\end{align}
\end{proof}

>>>>

Note that a stable closed-loop model is not necessarily a safe model: 
indeed, the state values may leave the safe part of the state space while they converge
to the equilibrium, which is typical in the case of oscillatory and convergent dynamics. 
%However, a safe system will always be stable.  
In~this work, the safety property is expressed as the formula:
%
\begin{equation}
\label{eq:safetyliteral}
\phi_\mathit{safety} := \forall k\ge 0.\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
\end{equation}
%
%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
%
where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$, ranging over the $k$-th time step.  
This means that the states are required to remain within an $n$-dimensional hyper-box at any point in time.

@@

We analyze the case of hybrid-time models, 
namely where the plant dynamics evolve in continuous time, 
while the feedback dynamics evolve in discrete time.  
A new input value is accepted by the plant only at sample times $T_s$. \note{Confusing use of $T_s$ vs $T_d$ - please clarify.} 
%but implemented over the continuous-time plant dynamics.
%
%\note{Matrix K has not been introduced yet. }
\begin{theorem}
The expression
%
 \begin{align}
 \vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0, 
 \label{eq:cyber_feedback}
 \end{align}
%
with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}, $\mat{B}_T$ as in
\eqref{eq:continuous_tube_param}, and where $\mat{A}_d=\mat{A}_{T_s}$,
$\mat{B}_d=\mat{B}_{T_s}$ describe the discretized plant dynamics with
sample time $T_s$, is the state of the model
%
\begin{align*}
 \dot{\vec{x}}(t) = \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t), \quad 
 \vec{u}(t)=\mat{K}\vec{x}_k,  \,
 kT_s \leq t < (k+1)T_s \,. 
\end{align*}
%
\end{theorem}
\begin{proof}
\note{let us not number the proofs.}
%
Let $\mat{K}$ be a feedback controller such that
$\vec{u}_k=-\mat{K}\vec{x}_k$ at time $t=kT_s$.  Let the output of the
feedback system be a zero order holder such that
$\vec{u}(t'+kT_s)=\vec{u}(kT_s), \text{ for } 0 \leq t' < T_s$.  The closed
loop dynamics of the system between times $kT_s$ and $kT_s+T_s$ are
%
\begin{align*}
\vec{x}_{k,t'}=\mat{A}_{t'}\vec{x}_k-\mat{B}_{t'}\mat{K}\vec{x}_k = (\mat{A}_{t'}-\mat{B}_{t'}\mat{K})\vec{x}_k,
\end{align*}
where $0 \leq t' < T_s$
We further explore the dynamics across discrete time boundaries. Let $\mat{A}_d=\mat{A}_{T_s}$ and $\mat{B}_d=\mat{B}_{T_s}$
\begin{align*}
\vec{x}_{k}&=\vec{x}_{k-1,T_s}= (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}\\
\vec{x}_{k,T_s} &= (\mat{A}_d-\mat{B}_d\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}
\end{align*}
which accelerating results and setting $T=kT_s+t'$ becomes
\begin{align}
\label{eq:feedback_sampled_cont}
\vec{x}_{k} &= (\mat{A}_d-\mat{B}_d\mat{K}) ^k\vec{x}_0\\
\vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
\label{eq:feedback_cont}
\end{align}
\end{proof}
